Differentially Private Bayesian Inference

### 2018-07-07 main.tex
update theory analysis

\begin{definition} The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
\end{equation*}
where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(y),-)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

@@

\section{Accuracy Analysis}
\subsection{Laplace Mechanism}
Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
\end{equation*}

@@

\subsection{Exponential Mechanism with Global Sensitivity}
Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
\end{equation*}
where $|R|$ is the size of the candidate set. Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$

\subsection{Exponential Mechanism with Smooth Sensitivity}
We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.

@@

\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately. In following analysis, we will count the probabilities wrt. the steps from correct answer, in order to be more concise and comparable to the experiment results from Sec. \ref{subsec_accuracy_hellinger}. For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$. Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer. i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$. This will make the results more clear and observable.

@@

@@

\subsubsection{Accuracy Analysis wrt. prior distribution}

\section{Experimental Evaluations}
\label{experiment}

@@

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsubsec_vs_variables}

@@

\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
\label{subsec_vs_prior_variance}

>>>>

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
\end{equation*}
where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(y),-)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

@@

\section{Accuracy Analysis}
\subsection{Laplace Mechanism}
\label{subsec_accuracy_lap}
Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
\end{equation*}

@@

\subsection{Exponential Mechanism with Global Sensitivity}
\label{subsec_accuracy_global}
Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
\end{equation*}
where $|R|$ is the size of the candidate set. Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$

\subsection{Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_smoo}
We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.

@@

\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately. In following analysis, we will count the probabilities wrt. the steps from correct answer, in order to be more concise. For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$. Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer. i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$. This will make the results more clear and observable.

@@

\subsubsection{Accuracy Analysis wrt. prior distribution}
In this part, we firstly study the local sensitivity of Hellinger distance of different $\betad$ distributions as in Fig. \ref{fig_sensitivity}, in order to have a better understanding of the relationships between accuracy and next two aspects.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{sensitivity}
\label{fig_sensitivity}
\caption{Hellinger distance study}
\end{figure}

As in Fig. \ref{fig_sensitivity}, the local sensitivity of Hellinger distance will decrease when $\betad$ distribution's two parameters get closer (i.e. more uniform) and larger. In the same time, our smooth sensitivity will also decrease based on the Def. \ref{def_smoo}. From accuracy bound in Sec. \ref{subsec_accuracy_smoo}, the accuracy will be improved when sensitivity go larger. In consequence, when we increase the prior distribution, the smooth sensitivity in our exponential mechanism will decrease, which means our accuracy will be improved. However, the sensitivity of $l_1$ norm in Laplace mechanism is fixed regardless the prior distribution. We will study this trade-off in Sec. \ref{subsubsec_vs_prior}.

Similar as above, when the data variance is small (i.e. the data are uniform), the parameters of posterior distribution will get more uniform (i.e. closer). Based on Fig. \ref{fig_sensitivity}, the Hellinger distance's sensitivity will get smaller when parameter get closer. As a result, the accuracy will be improved in the same time. We will study this trade-off in Sec. \ref{subsubsec_vs_variance}

@@

\section{Experimental Evaluations}
\label{sec_experiment}

@@

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsec_vs_variables}

@@

\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
\label{subsubsec_vs_prior_variance}
